Equations & R Code

### 2016-11-09 manuscript/coexistence-stability_ms.Rmd
updates results and discussion; ms sent to PBA

Under relative nonlinearity, species' resource response curves (Fig. SX) reflect traits that determine the intrinsic stability of each species.
Therefore, we ran two sets of simulations for relative nonlinearity: one where the species pools increased from stable to unstable species and vice versa.
For example, if species A is the most stable species and species D is the least stable we ran simulations where the species pool increased from one to four species as A then B then C then D.
We then ran simulations with that order reversed.

All simulations were run for 5,000 seasons with 20-day growing seasons. 
We averaged biomass over the growing season, and those yearly values were used to calculate total community biomass in each year.
After discarding an initial 500 seasons to reduce transient effects on our results, we calculated the coffecient of variation (*CV*) of summed species biomass through time, which represents ecosystem variability,  the inverse of ecosystem stability.
We calculated species richness as the number of species whose average biomass was greater than 1 over the course of the simulation.
Parameter values for specific results are given in figure captions.
Within-season dynamics were solved given initial conditions using the package ``deSolve`` [@Soetaert2010] in ``R`` [@Team2013].
All model code has been deposited on Figshare (*link*) and is available on GitHub at http://github.com/atredennick/Coexistence-Stability.

RESULTS
-------
Our simulation experiments show that the direction of the diversity-variability relationship can be positive or negative when species coexistence is maintained by fluctuation-dependent mechanisms (Fig. 2).
Ecosystem variability is positively correlated with species richness when species richness is measured across a gradient of environmental variability. 
The variability promotes diversity (Fig. SX) but also leads to increased ecosystem variability (Fig. 2A,C).
On the other hand, holding environmental conditions constant (but at levels sufficient for coexistence), removing species increases ecosystem variability (Fig. 2B,D).

DISCUSSION
----------
### The diversity-variability relationship
Theory developed for biodiversity-ecosystem function experiments emphasizes that increases in species richness should reduce ecosystem variability. , consistent with theoretical expectations from models in which species coexistence maintained by fluctuation-dependent mechanisms, and consistent with Species almost certainly coexist by some combination of fluctuation-independent (e.g., resource partitioning) and fluctuation-dependent mechanisms.
By extending theory to communities where species richness is explicitly maintained by temporal variability, we have gained confidence that experimental findings are generalizable to many communities.
In other words, in local settings where environmental variability is relatively homogenous, reductions in the number of species will reduce the stability of ecosystem functioning, regardless of how coexistence is maintained.

@@

### The impact of increasing environmental variability on ecosystem variability
Whether coexistence is fluctuation-independent or fluctuation-dependent becomes especially important when we consider how ecosystem stability responds to increasing environmental variability.
In the fluctuation-independent case, species richness is essentially fixed because the species' inequalities that determine coexistence (niche and fitness differences) are not linked to environmental variability.
Therefore, increasing environmental variability will always increase ecosystem variability by increasing the fluctuations of individual species' abundances.

When species coexistence is fluctuation-dependent via the storage effect, increasing environmental variability has much more interesting effects on ecosystem variability.
In Fig. 3 we show storage effect simulation results where environmental variability determines species coexistence from a regional species pool of four species.
We also show results from nested subsets of the four species pool (e.g., only two species in the pool instead of four) to show the trajectory of ecosystem variability if new species are not present to join the local community.
In accordance with coexistence theory, we find that realized species richness increases with environmental variability and, in some cases, increasing variability can actually completely temper the effect of increasing environmental variability.
More species rich communities are less variable on average (e.g., lower intercepts in log-log space; Fig. SX) and increase in ecosystem *CV* at a slower rate (e.g., lower slopes in log-log space; Fig. SX).

The dampening effect of fluctuation-dependent coexistence on increasing environmental variability depends on the specific traits (parameter values) of the species in the regional pool.
Asymmetric competition makes it more difficult for new species to enter the local community (Fig. 3; compare top and bottom panels).
Relatively high competition also increases the rate at which ecosystem *CV* increases with environmental variance (Fig. SX).
This is because the abundance of inferior competitors is reduced and therefore does not influence ecosystem *CV* as much as when competition is symmetric.
The correlation of species' environmental responses also mediates the relationship between environmental variance, species richness, and ecosystem *CV*: lower correlations make it easier for new species to coexist and unique environmental responses are always stabilizing (Fig. 3).

In communities where species coexist via relative nonlinearity, whether or not the direct impact of environmental variability on ecosystem variability is tempered by species additions depends on the species traits of immigrating species.
When additional species, which immigrate from the regional pool, are less intrinsically stable than the resident species, ecosystem variability increases at a constant rate even as species are added (Fig. 4A).
On the contrary, if more stable species are added, species additions buffer the ecosystem from increasing environmental variability (Fig. 4B).
The stability of individual species in our relative nonlinearity model is determined by their respective resource response curves (Fig. SX).
Under relative nonlinearity, we find that the buffering effect of species additions depends on species traits, and the order in which species enter the local community.
Indeed, if all species in the regional pool are less stable than the resident species, then no stabilization occurs as species are added (Fig. 4A).

Our simulation results lead to two conclusions.
First, when predicting the impacts of increasing environmental variability on ecosystem stability, the mechanism of coexistence in the community matters.
Fluctuation-dependent coexistence can buffer ecosystems from increasing environmental variability by allowing for species additions.
As shown in previous work [@Loreau2013], the stabilizing effect of species additions depends on the correlations of their environmental responses (Fig. 3e-f).
Whether our theoretical predictions hold in real communities is unknown and requires empirical tests.
Doing so would require manipulating environmental variability in communities where coexistence is known to be fluctuation-dependent, at least in part.
Such data do exist [@Angert2009], and a coupled modeling-experimental approach could determine if our predictions hold true in real communities.

@@

CONCLUSIONS
-----------
How does fluctuation-dependent coexistence affect the diversity-stability relationship?
At a given level of environmental variability, the typical positive diversity-stability relationship holds because having more species always stabilizes ecosystem functioning.
However, counter to other theoretical studies, we found that a negative diversity-stability relationship is also possible if sampling occurs across a natural diversity gradient and species coexistence is dependent on environmental fluctuations.
We also found that fluctuation-dependent species coexistence may help buffer ecosystems from increasing environmental variability because environmental variability promotes species richness, which, in turn, promotes stability.
Where fluctuation-dependent species coexistence prevails and environmental variability is projected to increase, our findings suggest that conserving regional species pools and dispersal corridors between local communities will be important.

>>>>

Under relative nonlinearity, species' resource response curves (Fig. S1-1) reflect traits that determine the intrinsic stability of each species.
Therefore, we ran two sets of simulations for relative nonlinearity: one where the species pools increased from stable to unstable species and vice versa.
For example, if species A is the most stable species and species D is the least stable we ran simulations where the species pool increased from one to four species as A then B then C then D.
We then ran simulations with that order reversed.

All simulations were run for 5,000 seasons with 20-day growing seasons. 
We averaged biomass over the growing season, and those yearly values were used to calculate total community biomass in each year.
After discarding an initial 500 seasons to reduce transient effects on our results, we calculated the coffecient of variation (*CV*) of summed species biomass through time, which represents ecosystem variability,  the inverse of ecosystem stability.
We calculated species richness as the number of species whose average biomass was greater than 1 over the course of the simulation.
Parameter values for specific results are given in figure captions.
Within-season dynamics were solved given initial conditions using the package ``deSolve`` [@Soetaert2010] in ``R`` [@Team2013].
```R``` code for our model function is in the Supporting Information Appendix S1.
All model code has been deposited on Figshare (*link*) and is available on GitHub at http://github.com/atredennick/Coexistence-Stability.

RESULTS
-------
When we allowed the variance of the environment to determine the number of coexisting species from an initial community of four, we found a positive relationship between diversity and variability (Fig. 2A,C).
This was true for the storage effect, where coexistence is maintained by fluctuating transition rates ($\gamma$), and for relative nonlinearity, where coexistence is maintained by annual resource pulses.
The relationship is driven by the fact that, under both coexistence mechanisms, the strength of species coexistence increased with environmental variability (Fig. S1-2).
Therefore, more variabile conditions promoted species richness, creating a positive relationship between diversity and variability.

When we performed species removals at given levels of environmental variability, we found the typical negative diversity-variability relationship (Fig. 2B,D).
The relationship is very constrained for the storage effect because all species have similar temporal variances.
Therefore, regardless of species identity, having more species will always stabilize ecosystem functioning through portfolio effects.
On the contrary, the relationship is less strong for relative nonlinearity (Fig. 2D) because each species has unique temporal variance depending on its resource uptake curve.
Depending on the specific combination of species, two-species communities may sometimes be less variable than three-species communities.

To analyze the above results in more detail, we simulated our model over range of environmental variance and species pool sizes.
In Fig. 3 we show storage effect simulation results where environmental variability determines species coexistence from a regional species pool of four species.
We also show results from nested subsets of the four species pool (e.g., only two species in the pool instead of four) to show the trajectory of ecosystem variability if new species are not present to join the local community.
We find that realized species richness increases with environmental variability and, in some cases, increasing variability can actually completely temper the effect of increasing environmental variability.
More species rich communities are less variable on average and increase in ecosystem *CV* at a slower rate (e.g., lower slopes in log-log space; Fig. S1-3).

The dampening effect of fluctuation-dependent coexistence on increasing environmental variability depends on the specific traits (parameter values) of the species in the regional pool.
Asymmetric competition makes it more difficult for new species to enter the local community (Fig. 3; compare top and bottom panels).
Relatively high competition also increases the rate at which ecosystem *CV* increases with environmental variance (Fig. S1-3).
This is because the abundance of inferior competitors is reduced and therefore does not influence ecosystem *CV* as much as when competition is symmetric.
The correlation of species' environmental responses also mediates the relationship between environmental variance, species richness, and ecosystem *CV*: lower correlations make it easier for new species to coexist and unique environmental responses are always stabilizing (Fig. 3).

In communities where species coexist via relative nonlinearity, whether or not the direct impact of environmental variability on ecosystem variability is tempered by species additions depends on the species traits of immigrating species.
When additional species, which immigrate from the regional pool, are less intrinsically stable than the resident species, ecosystem variability increases at a constant rate even as species are added (Fig. 4A).
On the contrary, if more stable species are added, species additions buffer the ecosystem from increasing environmental variability (Fig. 4B).
The stability of individual species in our relative nonlinearity model is determined by their respective resource response curves (Fig. S1-1).
Under relative nonlinearity, we find that the buffering effect of species additions depends on species traits, and the order in which species enter the local community.
Indeed, if all species in the regional pool are less stable than the resident species, then no stabilization occurs as species are added (Fig. 4A).

DISCUSSION
----------
Theory developed for biodiversity-ecosystem function experiments emphasizes that increases in species richness should reduce ecosystem variability. 
Consistent with theoretical expectations from models in which species coexistence is maintained by fluctuation-independent mechanisms, we produced the typical negative diversity-variability relationship (Fig. 2B,D) from a model with fluctation-dependent species coexistence [also see @Chesson2001].
Likewise, our results from the species removal simulations are consistent with results from biodiversity-ecosystem functioning experiments showing a negative relationship between species richness and ecosystem variability.
This is encouraging because species almost certainly coexist by some combination of fluctuation-independent (e.g., resource partitioning) and fluctuation-dependent mechanisms.
By extending theory to communities where species richness is explicitly maintained by temporal variability, we have gained confidence that experimental findings are generalizable to many communities.
In other words, in local settings where environmental variability is relatively homogenous, reductions in the number of species will reduce the stability of ecosystem functioning, regardless of how coexistence is maintained.

When we allowed a gradient of environmental variability to determine species coexistence, we discovered a positive relationship between species richness and ecosystem variability (Fig. 2A,C).
While surprising when viewed through the lens of previous theory and experimental findings, such a relationship is a direct consequence of how diversity can be maintained in fluctuating environments.
The storage effect and relative nonlinearity both require envrionmental fluctuations to allow niche differentiation between species pairs [@Chesson2000].
Therefore, species coexistence gains strength, for both mechanisms, as the environment becomes more variable (Fig. S1-2).

@@

Whether coexistence is fluctuation-independent or fluctuation-dependent becomes especially important when we consider how ecosystem stability responds to increasing environmental variability.
In the fluctuation-independent case, species richness is essentially fixed because the species' inequalities that determine coexistence (niche and fitness differences) are not linked to environmental variability.
Therefore, increasing environmental variability will always increase ecosystem variability by increasing the fluctuations of individual species' abundances.

When coexistence is fluctuation-dependent, however, more interesting things happen.
By simulating communities with different species pool sizes across a gradient of environmental variabilitym, we show that species gains due to increasing environmental variability can temper the direct effect of environmental variability on ecosystem variability (Figs. 3 and 4).
These results lead to two conclusions.

First, when predicting the impacts of increasing environmental variability on ecosystem stability, the mechanism of coexistence in the community matters.
Fluctuation-dependent coexistence can buffer ecosystems from increasing environmental variability by allowing for species additions.
Whether our theoretical predictions hold in real communities is unknown and requires empirical tests.
Doing so would require manipulating environmental variability in communities where coexistence is known to be fluctuation-dependent, at least in part.
Such data do exist [@Angert2009], and a coupled modeling-experimental approach could determine if our predictions hold true in real communities.

@@

### 2016-11-09 manuscript/coexistence-stability_ms.tex
updates results and discussion; ms sent to PBA

Under relative nonlinearity, species' resource response curves (Fig. SX)
reflect traits that determine the intrinsic stability of each species.
Therefore, we ran two sets of simulations for relative nonlinearity: one
where the species pools increased from stable to unstable species and
vice versa. For example, if species A is the most stable species and
species D is the least stable we ran simulations where the species pool
increased from one to four species as A then B then C then D. We then
ran simulations with that order reversed.

All simulations were run for 5,000 seasons with 20-day growing seasons.
We averaged biomass over the growing season, and those yearly values
were used to calculate total community biomass in each year. After
discarding an initial 500 seasons to reduce transient effects on our
results, we calculated the coffecient of variation (\emph{CV}) of summed
species biomass through time, which represents ecosystem variability,
the inverse of ecosystem stability. We calculated species richness as
the number of species whose average biomass was greater than 1 over the
course of the simulation. Parameter values for specific results are
given in figure captions. Within-season dynamics were solved given
initial conditions using the package \texttt{deSolve} (Soetaert et al.
2010) in \texttt{R} (Team 2013). All model code has been deposited on
Figshare (\emph{link}) and is available on GitHub at
\url{http://github.com/atredennick/Coexistence-Stability}.

@@

Our simulation experiments show that the direction of the
diversity-variability relationship can be positive or negative when
species coexistence is maintained by fluctuation-dependent mechanisms
(Fig. 2). Ecosystem variability is positively correlated with species
richness when species richness is measured across a gradient of
environmental variability. The variability promotes diversity (Fig. SX)
but also leads to increased ecosystem variability (Fig. 2A,C). On the
other hand, holding environmental conditions constant (but at levels
sufficient for coexistence), removing species increases ecosystem
variability (Fig. 2B,D).

@@

\subsubsection{The diversity-variability
relationship}\label{the-diversity-variability-relationship}

Theory developed for biodiversity-ecosystem function experiments
emphasizes that increases in species richness should reduce ecosystem
variability. , consistent with theoretical expectations from models in
which species coexistence maintained by fluctuation-dependent
mechanisms, and consistent with Species almost certainly coexist by some
combination of fluctuation-independent (e.g., resource partitioning) and
fluctuation-dependent mechanisms. By extending theory to communities
where species richness is explicitly maintained by temporal variability,
we have gained confidence that experimental findings are generalizable
to many communities. In other words, in local settings where
environmental variability is relatively homogenous, reductions in the
number of species will reduce the stability of ecosystem functioning,
regardless of how coexistence is maintained.

@@

\subsubsection{The impact of increasing environmental variability on
ecosystem
variability}\label{the-impact-of-increasing-environmental-variability-on-ecosystem-variability}

@@

When species coexistence is fluctuation-dependent via the storage
effect, increasing environmental variability has much more interesting
effects on ecosystem variability. In Fig. 3 we show storage effect
simulation results where environmental variability determines species
coexistence from a regional species pool of four species. We also show
results from nested subsets of the four species pool (e.g., only two
species in the pool instead of four) to show the trajectory of ecosystem
variability if new species are not present to join the local community.
In accordance with coexistence theory, we find that realized species
richness increases with environmental variability and, in some cases,
increasing variability can actually completely temper the effect of
increasing environmental variability. More species rich communities are
less variable on average (e.g., lower intercepts in log-log space; Fig.
SX) and increase in ecosystem \emph{CV} at a slower rate (e.g., lower
slopes in log-log space; Fig. SX).

The dampening effect of fluctuation-dependent coexistence on increasing
environmental variability depends on the specific traits (parameter
values) of the species in the regional pool. Asymmetric competition
makes it more difficult for new species to enter the local community
(Fig. 3; compare top and bottom panels). Relatively high competition
also increases the rate at which ecosystem \emph{CV} increases with
environmental variance (Fig. SX). This is because the abundance of
inferior competitors is reduced and therefore does not influence
ecosystem \emph{CV} as much as when competition is symmetric. The
correlation of species' environmental responses also mediates the
relationship between environmental variance, species richness, and
ecosystem \emph{CV}: lower correlations make it easier for new species
to coexist and unique environmental responses are always stabilizing
(Fig. 3).

In communities where species coexist via relative nonlinearity, whether
or not the direct impact of environmental variability on ecosystem
variability is tempered by species additions depends on the species
traits of immigrating species. When additional species, which immigrate
from the regional pool, are less intrinsically stable than the resident
species, ecosystem variability increases at a constant rate even as
species are added (Fig. 4A). On the contrary, if more stable species are
added, species additions buffer the ecosystem from increasing
environmental variability (Fig. 4B). The stability of individual species
in our relative nonlinearity model is determined by their respective
resource response curves (Fig. SX). Under relative nonlinearity, we find
that the buffering effect of species additions depends on species
traits, and the order in which species enter the local community.
Indeed, if all species in the regional pool are less stable than the
resident species, then no stabilization occurs as species are added
(Fig. 4A).

Our simulation results lead to two conclusions. First, when predicting
the impacts of increasing environmental variability on ecosystem
stability, the mechanism of coexistence in the community matters.
Fluctuation-dependent coexistence can buffer ecosystems from increasing
environmental variability by allowing for species additions. As shown in
previous work (Loreau and {{de Mazancourt}} 2013), the stabilizing
effect of species additions depends on the correlations of their
environmental responses (Fig. 3e-f). Whether our theoretical predictions
hold in real communities is unknown and requires empirical tests. Doing
so would require manipulating environmental variability in communities
where coexistence is known to be fluctuation-dependent, at least in
part. Such data do exist (Angert et al. 2009), and a coupled
modeling-experimental approach could determine if our predictions hold
true in real communities.

@@

\subsection{CONCLUSIONS}\label{conclusions}

How does fluctuation-dependent coexistence affect the
diversity-stability relationship? At a given level of environmental
variability, the typical positive diversity-stability relationship holds
because having more species always stabilizes ecosystem functioning.
However, counter to other theoretical studies, we found that a negative
diversity-stability relationship is also possible if sampling occurs
across a natural diversity gradient and species coexistence is dependent
on environmental fluctuations. We also found that fluctuation-dependent
species coexistence may help buffer ecosystems from increasing
environmental variability because environmental variability promotes
species richness, which, in turn, promotes stability. Where
fluctuation-dependent species coexistence prevails and environmental
variability is projected to increase, our findings suggest that
conserving regional species pools and dispersal corridors between local
communities will be important.

>>>>

Under relative nonlinearity, species' resource response curves (Fig.
S1-1) reflect traits that determine the intrinsic stability of each
species. Therefore, we ran two sets of simulations for relative
nonlinearity: one where the species pools increased from stable to
unstable species and vice versa. For example, if species A is the most
stable species and species D is the least stable we ran simulations
where the species pool increased from one to four species as A then B
then C then D. We then ran simulations with that order reversed.

All simulations were run for 5,000 seasons with 20-day growing seasons.
We averaged biomass over the growing season, and those yearly values
were used to calculate total community biomass in each year. After
discarding an initial 500 seasons to reduce transient effects on our
results, we calculated the coffecient of variation (\emph{CV}) of summed
species biomass through time, which represents ecosystem variability,
the inverse of ecosystem stability. We calculated species richness as
the number of species whose average biomass was greater than 1 over the
course of the simulation. Parameter values for specific results are
given in figure captions. Within-season dynamics were solved given
initial conditions using the package \texttt{deSolve} (Soetaert et al.
2010) in \texttt{R} (Team 2013). \texttt{R} code for our model function
is in the Supporting Information Appendix S1. All model code has been
deposited on Figshare (\emph{link}) and is available on GitHub at
\url{http://github.com/atredennick/Coexistence-Stability}.

@@

When we allowed the variance of the environment to determine the number
of coexisting species from an initial community of four, we found a
positive relationship between diversity and variability (Fig. 2A,C).
This was true for the storage effect, where coexistence is maintained by
fluctuating transition rates (\(\gamma\)), and for relative
nonlinearity, where coexistence is maintained by annual resource pulses.
The relationship is driven by the fact that, under both coexistence
mechanisms, the strength of species coexistence increased with
environmental variability (Fig. S1-2). Therefore, more variabile
conditions promoted species richness, creating a positive relationship
between diversity and variability.

When we performed species removals at given levels of environmental
variability, we found the typical negative diversity-variability
relationship (Fig. 2B,D). The relationship is very constrained for the
storage effect because all species have similar temporal variances.
Therefore, regardless of species identity, having more species will
always stabilize ecosystem functioning through portfolio effects. On the
contrary, the relationship is less strong for relative nonlinearity
(Fig. 2D) because each species has unique temporal variance depending on
its resource uptake curve. Depending on the specific combination of
species, two-species communities may sometimes be less variable than
three-species communities.

To analyze the above results in more detail, we simulated our model over
range of environmental variance and species pool sizes. In Fig. 3 we
show storage effect simulation results where environmental variability
determines species coexistence from a regional species pool of four
species. We also show results from nested subsets of the four species
pool (e.g., only two species in the pool instead of four) to show the
trajectory of ecosystem variability if new species are not present to
join the local community. We find that realized species richness
increases with environmental variability and, in some cases, increasing
variability can actually completely temper the effect of increasing
environmental variability. More species rich communities are less
variable on average and increase in ecosystem \emph{CV} at a slower rate
(e.g., lower slopes in log-log space; Fig. S1-3).

The dampening effect of fluctuation-dependent coexistence on increasing
environmental variability depends on the specific traits (parameter
values) of the species in the regional pool. Asymmetric competition
makes it more difficult for new species to enter the local community
(Fig. 3; compare top and bottom panels). Relatively high competition
also increases the rate at which ecosystem \emph{CV} increases with
environmental variance (Fig. S1-3). This is because the abundance of
inferior competitors is reduced and therefore does not influence
ecosystem \emph{CV} as much as when competition is symmetric. The
correlation of species' environmental responses also mediates the
relationship between environmental variance, species richness, and
ecosystem \emph{CV}: lower correlations make it easier for new species
to coexist and unique environmental responses are always stabilizing
(Fig. 3).

In communities where species coexist via relative nonlinearity, whether
or not the direct impact of environmental variability on ecosystem
variability is tempered by species additions depends on the species
traits of immigrating species. When additional species, which immigrate
from the regional pool, are less intrinsically stable than the resident
species, ecosystem variability increases at a constant rate even as
species are added (Fig. 4A). On the contrary, if more stable species are
added, species additions buffer the ecosystem from increasing
environmental variability (Fig. 4B). The stability of individual species
in our relative nonlinearity model is determined by their respective
resource response curves (Fig. S1-1). Under relative nonlinearity, we
find that the buffering effect of species additions depends on species
traits, and the order in which species enter the local community.
Indeed, if all species in the regional pool are less stable than the
resident species, then no stabilization occurs as species are added
(Fig. 4A).

@@

Theory developed for biodiversity-ecosystem function experiments
emphasizes that increases in species richness should reduce ecosystem
variability. Consistent with theoretical expectations from models in
which species coexistence is maintained by fluctuation-independent
mechanisms, we produced the typical negative diversity-variability
relationship (Fig. 2B,D) from a model with fluctation-dependent species
coexistence (also see Chesson et al. 2001). Likewise, our results from
the species removal simulations are consistent with results from
biodiversity-ecosystem functioning experiments showing a negative
relationship between species richness and ecosystem variability. This is
encouraging because species almost certainly coexist by some combination
of fluctuation-independent (e.g., resource partitioning) and
fluctuation-dependent mechanisms. By extending theory to communities
where species richness is explicitly maintained by temporal variability,
we have gained confidence that experimental findings are generalizable
to many communities. In other words, in local settings where
environmental variability is relatively homogenous, reductions in the
number of species will reduce the stability of ecosystem functioning,
regardless of how coexistence is maintained.

When we allowed a gradient of environmental variability to determine
species coexistence, we discovered a positive relationship between
species richness and ecosystem variability (Fig. 2A,C). While surprising
when viewed through the lens of previous theory and experimental
findings, such a relationship is a direct consequence of how diversity
can be maintained in fluctuating environments. The storage effect and
relative nonlinearity both require envrionmental fluctuations to allow
niche differentiation between species pairs (Chesson 2000a). Therefore,
species coexistence gains strength, for both mechanisms, as the
environment becomes more variable (Fig. S1-2).

@@

@@

When coexistence is fluctuation-dependent, however, more interesting
things happen. By simulating communities with different species pool
sizes across a gradient of environmental variabilitym, we show that
species gains due to increasing environmental variability can temper the
direct effect of environmental variability on ecosystem variability
(Figs. 3 and 4). These results lead to two conclusions.

First, when predicting the impacts of increasing environmental
variability on ecosystem stability, the mechanism of coexistence in the
community matters. Fluctuation-dependent coexistence can buffer
ecosystems from increasing environmental variability by allowing for
species additions. Whether our theoretical predictions hold in real
communities is unknown and requires empirical tests. Doing so would
require manipulating environmental variability in communities where
coexistence is known to be fluctuation-dependent, at least in part. Such
data do exist (Angert et al. 2009), and a coupled modeling-experimental
approach could determine if our predictions hold true in real
communities.

@@
